### 2024-07-21 data-visualization.qmd
20240721 - conditional content
20240721 - attempt to fix error

@@

ggplot2::ggplot(
  data = rb_yardsPerCarry,
  aes(
    x = age,
    y = ypc)) +
  geom_point() +
  geom_smooth() +
  labs(
    x = "Rushing Back Age (years)",
    y = "Rushing Yards per Carry/season",
    title = "NFL Rushing Yards Per Carry per Season by Player Age",
    subtitle = "(minimum 50 rushing attempts)"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_epa)) +
  geom_point() +
  geom_smooth() +
  labs(
    x = "Rushing Back Age (years)",
    y = "Rushing EPA/season",
    title = "NFL Rushing Expected Points Added (EPA) per Season by Player Age"
  ) +
  theme_classic()
```

>>>>

::: {.content-visible when-format="html:js"}

After creating our plot, we can make the plot interactive using the `ggplotly()` function from the plotly package, as in @fig-scatterplot11.

```{r}
#| label: fig-scatterplot11
#| fig-cap: "Interactive Scatterplot Using Plotly."

plot_ypcByPlayerAge <- ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point(
    aes(
      text = player_display_name, # add player name for mouse over tooltip
      label = season)) + # add season for mouse over tooltip
  geom_smooth() +
  scale_x_continuous(
    expand = c(0,0),
    lim = c(20,40),
    breaks = seq(from = 20, to = 40, by = 5)
  ) +
  scale_y_continuous(
    expand = c(0,0),
    lim = c(0,NA),
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs(
    x = "Running Back Age (years)",
    y = "Rushing Yards Per Season",
    title = "2023 NFL Rushing Yards Per Carry per Season by Player Age",
    subtitle = "(minimum 50 rushing attempts)"
  ) +
  theme_classic()

ggplotly(plot_ypcByPlayerAge)
```

::: {.content-visible when-format="pdf"}

After creating our plot, we can make the plot interactive using the `ggplotly()` function from the plotly package.

```{r}
#| eval: false

plot_ypcByPlayerAge <- ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point(
    aes(
      text = player_display_name, # add player name for mouse over tooltip
      label = season)) + # add season for mouse over tooltip
  geom_smooth() +
  scale_x_continuous(
    expand = c(0,0),
    lim = c(20,40),
    breaks = seq(from = 20, to = 40, by = 5)
  ) +
  scale_y_continuous(
    expand = c(0,0),
    lim = c(0,NA),
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs(
    x = "Running Back Age (years)",
    y = "Rushing Yards Per Season",
    title = "2023 NFL Rushing Yards Per Carry per Season by Player Age",
    subtitle = "(minimum 50 rushing attempts)"
  ) +
  theme_classic()

ggplotly(plot_ypcByPlayerAge)
```

@@

ggplot2::ggplot(
  data = rb_yardsPerCarry,
  aes(
    x = age,
    y = ypc)) +
  geom_point(
    aes(
      text = player_display_name,
      label = season)) +
  geom_smooth() +
  labs(
    x = "Rushing Back Age (years)",
    y = "Rushing Yards per Carry/season",
    title = "NFL Rushing Yards Per Carry per Season by Player Age",
    subtitle = "(minimum 50 rushing attempts)"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_epa)) +
  geom_point(
    aes(
      text = player_display_name,
      label = season)) +
  geom_smooth() +
  labs(
    x = "Rushing Back Age (years)",
    y = "Rushing EPA/season",
    title = "NFL Rushing Expected Points Added (EPA) per Season by Player Age"
  ) +
  theme_classic()
```
